Object Maker

### 2015-02-28 dataCleaning.Rmd
Major update.

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

#Creates data frames that contain only article ID and titles from respective
#databases
ebscoTitles<-filter(ebscoBWR.df, attributes=="article")
proTitles<-filter(proQuestBWR.df, attributes=="article")

#Combines titles into single data frame
jointTitles<-rbind(ebscoTitles, proTitles)

#Forces article title text to lower case
jointTitles$record<-tolower(jointTitles$record)

#Strips out white space and punctuation to ensure small differences in data 
#entry are detected during duplicate elimination
jointTitles$record<-gsub(" ","", jointTitles$record)

jointTitles$record<-gsub("[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]", "", jointTitles$record)

jointTitles<- jointTitles[duplicated(jointTitles$record), ]

#Screen out duplicated records by articleID. The articleID must be used
#because the duplicate title contains other article attributes
jointTitles.dup.ID <- jointTitles$articleID

  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
  #from duplicate entries
  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
  full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

@@

@@

```{r}

year.25 <- as.character(c(1900:1987, 2014, 2015))
years <- c("2014", "2015")
#ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- full.df[full.df$record %in% year.25, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

@@

@@

rm(ebsco.remove)
```

@@

```{r date, echo=FALSE, comment=NA}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
print.data.frame(unique.titles, rowNames=FALSE)
```

@@

>>>>

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
```

@@

full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
```

```{r reduced, comment=NA}
titles <- filter(full.df, attributes == "article")
journals <- filter(full.df, attributes == "journal")
year <- filter(full.df, attributes == "pubYear")

year.journal <- dplyr::intersect(year$articleID, journals$articleID)
year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)

full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
```

Exclude incorrectly captured articles. 
```{r}
#Identify records that were incorrectly captured in the wrangle
#using regular expressions
insert.1<-"[B|b]ook [R|r]eview[.:]|^[F|f]orum.+|[F|f]orum$|[C|c]ommentary|Comment.+"
insert.2<-"^[I|i]ndex\\s[T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndetermined"
insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
             ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
            ^Volume.+ | ^\\["
insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6, 
              insert.7, sep="|")

badRecords<-subset(titles, grepl(insert, record))
badRecords.ID<-badRecords$articleID

full.df <- full.df[!(full.df$articleID %in% badRecords.ID), ]

@@

Duplicate title search
```{r}
titles$matching <- tolower(titles$record)

#Eliminate `the` and `a` at the beginning of sentences and after colons
titles$matching <- gsub("^the\\s", "", titles$matching)
titles$matching <- gsub("^a\\s", "", titles$matching)
titles$matching <- gsub("[[:punct:]]", "", titles$matching)

#Strips out white space and punctuation to ensure small differences in data 
#entry are detected during duplicate elimination
titles$matching <- gsub(" ","", titles$matching)

duplicated.titles <- duplicated(titles$matching)
duplicated.ID <- titles$articleID[duplicated.titles]
full.df <- full.df[!(full.df$articleID %in% duplicated.ID), ]
```

@@

```{r}
year.25 <- as.character(c(1900:1987, 2014, 2015))

temp.df <- filter(full.df, attributes == "pubYear")

year.remove <- temp.df[temp.df$record %in% year.25, ]
year.removeID <- year.remove$articleID

full.df <- full.df[!(full.df$articleID %in% year.removeID), ]

@@

dim(filter(full.df, attributes == "pubYear"))
dim(filter(full.df, attributes == "article"))
dim(filter(full.df, attributes == "journal"))

@@

rm(ebsco.remove)

```{r echo=FALSE, comment=NA}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
print.data.frame(unique.titles, rowNames=FALSE)
```

@@

```{r echo=FALSE, comment=NA}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
print.data.frame(unique.titles, rowNames=FALSE)
```

@@

articles <- filter(full.df, attributes == "article") %>% arrange(record)
write.csv(articles, file = "articles.csv")

### 2015-02-28 objectMaker.Rmd
Fixed minor bugs.
Major update.

ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=FALSE)
save(ebscoBWR.df, file = "ebscoFULL.R")
```

@@

@@

ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=TRUE)
save(ebscoBWR.df, file = "PsychInfo.R")
```

>>>>

ebscoBWR.f(csv=FALSE, path=path)
save(ebscoBWR.df, file = "ebscoFULL.R")
```

@@

```{r warning=FALSE, message=FALSE, eval=FALSE}
# Clear workspace
rm(list=ls())

@@

ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=TRUE)
ebscoPsycInfoBWR.df <- ebscoBWR.df
save(ebscoPsycInfoBWR.df, file = "PsycInfo.R")
```
